Fully Automatic Loop-free Program Synthesis by Bounded Model Checking

### 2013-10-11 paper/paper.tex
Change size of results tables so they fit on 1 page
nudges conclusion

%\begin{figure}
% \includegraphics[width=\linewidth]{figures/brahma_kalashnikov.pdf}
% \caption{Brahma runtimes vs. Kalashnikov}
%  \label{fig:brahma-kalashnikov}

%\end{figure}

{\tiny
\begin{center}
 \begin{tabular}{r||r|r|r|r|r|r|r|r|r}
  & \multicolumn{3}{c}{Count} & \multicolumn{2}{|c}{Total time} & \multicolumn{2}{|c}{Absolute speedup} & \multicolumn{2}{|c}{Relative speedup} \\
  {\sc Brahma} version & Total & {\sc Kalashnikov} & {\sc Brahma} & {\sc Kalashnikov} & {\sc Brahma} & Mean & Median & Mean & Median \\
  &       & faster            & faster       &                   &              &      &        &      & \\
  \hline
  \hline
  PLDI & 16 & 13 & 3 & 184.12\,s & 544.20\,s & 22.50\,s & 2.11\,s & 2.60 & 1.77 \\
  ICSE Semibiased & 17 & 7 & 10 & 225.49\,s & 262.24\,s & 2.16\,s & -1.00\,s & 1.26 & 0.87
 \end{tabular}
\end{center}
}

 \caption{Performance statistics when {\sc Brahma} and {\sc Kalashnikov} were both successful
 \label{fig:stats-table}}
\end{figure}

@@

\paragraph{Future Work}
It may be possible to extend the language $\mathcal{L}$ with constructs such as branching and limited
looping while still retaining decidability, which would be an interesting direction to pursue.
Since our specification language is a subset of C, interfacing {\sc kalashnikov} with
other analysis tools should not be too difficult.  Various problems such as ranking function synthesis,
loop invariant generation and loop summarisation can be phrased as program synthesis problems,
and we would like to investigate the possiblities of applying {\sc kalashnikov} to these domains.

>>>>

\begin{figure}
{\tiny
\begin{center}
 \begin{tabular}{r||r|r|r|r|r|r|r|r|r}
  & \multicolumn{3}{c}{Count} & \multicolumn{2}{|c}{Total time} & \multicolumn{2}{|c}{Absolute speedup} & \multicolumn{2}{|c}{Relative speedup} \\
  {\sc Brahma} version & Total & {\sc Kalashnikov} & {\sc Brahma} & {\sc Kalashnikov} & {\sc Brahma} & Mean & Median & Mean & Median \\
  &       & faster            & faster       &                   &              &      &        &      & \\
  \hline
  \hline
  PLDI & 16 & 13 & 3 & 184.12\,s & 544.20\,s & 22.50\,s & 2.11\,s & 2.60 & 1.77 \\
  ICSE Semibiased & 17 & 7 & 10 & 225.49\,s & 262.24\,s & 2.16\,s & -1.00\,s & 1.26 & 0.87
 \end{tabular}
\end{center}
}

 \caption{Performance statistics when {\sc Brahma} and {\sc Kalashnikov} were both successful.
 \label{fig:stats-table}}
\end{figure}

@@

By expressing the program synthesis problem as a safety property for a
program interpreter, we have been able to harness the power of
state-of-the-art program analysis tools and reuse them in a new problem
domain.  We have implemented our algorithm as a freely downloadable tool
whose performance compares favourably to a recent program synthesiser. 
Finally, we have taken advantage of the expressiveness of our specification
language to make an initial step towards practical synthesis of
floating-point programs.

\paragraph{Future Work}

It may be possible to extend the language $\mathcal{L}$ with constructs such
as branching and limited looping while still retaining decidability, which
would be an interesting direction to pursue.  Since our specification
language is a subset of C, it is straight-forward to interface {\sc
kalashnikov} with other analysis tools.  Various problems such as ranking
function synthesis, loop invariant generation and loop summarisation can be
phrased as program synthesis problems, and we would like to investigate the
possiblities of applying {\sc kalashnikov} to these domains.
